### 2020-02-25 paper/revisions/review-responses.tex

        %---------------------------------------------------------------------

        \question In the SD-TMSR burnup calculation, how are the depletion regions and burnup time step defined?
        \begin{solution}

        		  Thank you for the excellent point.

        		  About depletion regions definition: we used the depletion mode 1 in SERPENT-2 (i.e. burn 1), which means that the fuel material
        		  is treated as a single depletion zone. The liquid fuel is well-mixed all the time due to turbulent flow and mixing in the pump.

        		  About burnup time step definition: it is time interval given in days. During burnup time step, the SD-TMSR core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%). We started our calculations by 30 days' time step but we do not find significant changes in $k_{eff}$ when we increased the time step to 365 days. The difference in $k_{eff}$ between $\Delta t=1$ year and $\Delta t=30$ days was $\leq$ 0.02\%; thus, we adopted a constant, 365-day-long time step for all simulation in this work.

@@

        		  We changed the paragraph as follows:\\

        		  The liquid fuel is well-mixed all the time due to turbulent flow and mixing in the pump. We used the depletion mode 1 in SERPENT-2 (i.e. burn 1), which means that the fuel material is treated as a single depletion zone.

        		  We changed the paragraph as follows:\\
        		  During the depletion step, the core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%). To determine the appropriate depletion step size, we conducted a time step refinement study. We started with $\Delta t=30$ days and gradually increased the depletion time step until the error in $k_{eff}$ became significant. The difference in $k_{eff}$ between $\Delta t=1$ year and $\Delta t=30$ days was $\leq$ 0.02\%; thus, we adopted a constant, 365-day-long time step for all simulation in this work.

@@

        \end{solution}

        %---------------------------------------------------------------------
        \question During the molten salt reactor operation, part of fuel salt flows outside of reactor core then the fission reaction is not happened in external loop, however the decay reactions happens everywhere. In other words, during one burnup step, the fission reactions occur in only part of the time (depends on the ratio of time taken in fuel salt passing reactor core and external loop), and nuclides' decay or other reactions occur in the whole burnup step time. Have you considered this in SERPENT calculation?  
        \begin{solution}

		          Thank you for your insightful comment. We used total fuel 
		          salt inventory in the primary loop to define the fuel 
		          material in the SERPENT input. Moreover, we accordingly 
		          adjusted power density in SERPENT burnup calculations 
		          because fission takes place only in the core region. But we did not consider processes, such as decay, which occurs outside of the core. Also, the drift of the delayed neutron precursors is not examined in this paper, but discussion about this can be found in Zhang et al. (2018) \cite{zhang2018review}.

		          During the molten salt reactor operation, part of fuel salt flows outside of the reactor core then the fission reaction has not happened in the external loop, however, the decay reactions happen everywhere. We used total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input. Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region. But we did not consider processes, such as decay, which occurs outside of the core. Also, the drift of the delayed neutron precursors is not examined in this paper, but discussion about this can be found in \cite{zhang2018review}.     
        \end{solution}

@@

                 Thank you for catching this. Reference 7 has been removed from the paragraph.

        \end{solution}

        %---------------------------------------------------------------------

        \question The authors did not conduct a sufficient literature survey on the fuel cycle transition studies for the SD-TMSR concept. Cui. et al., have made an extensive study on fuel cycle transition for SD-TMSR by employing LEU and Pu as the startup fissile materials and two transition modes (in-core transition and ex-core transition) (see Ref.: Transition toward thorium fuel cycle in a molten salt reactor by using plutonium, NUCL SCI TECH (2017) 28:152; Possible scenarios for the transition to thorium fuel cycle in molten salt reactor by using enriched uranium. Progress in Nuclear Energy 104 (2018) 75-84). The state "For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other fissile materials (except U-233) has not studied before" in page 3 is therefore inaccurate.
        \begin{solution}
                Thank you for your helpful review. The statement "For the SD-TMSR 
                concept, simulating the fissile core startup and fuel cycle 
                transition with other fissile materials (except$^{233}$U) has 
                not studied before" in page 3, has been removed. 
                The following paragraphs have been added to the manuscript:\\

                Cui \emph{et al.} analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design. Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% enrichment, which rises the proliferation concerns; (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel \cite{cui2017transition,cui2018possible}. The research effort described in \cite{cui2017transition} and
                \cite{cui2018possible} is most similar to the work
                presented in this paper. However, a few major differences
                are: (1) we used built-in truly continuous fuel depletion capabilities in
                SERPENT-2 \cite{aufiero2013extended} while Cui \emph{et al.} employed an in-house tool named MSR
                Reprocessing Sequence (MSR-RS) \cite{ZOU2015114} which couples with SCALE and employs a batch-wise approach (the burnup simulation stops at a given time and restarts with a new liquid fuel composition after removal of discarded materials and addition of fissile/fertile materials); (2) we investigated different initial loading cases (HALEU, Pu+HALEU, reactor-grade Pu, TRU and $^{233}$U) while Cui \emph{et al.} studied only uranium and Pu as the startup fissile materials; (3) we adopted the SD-TMSR core geometry optimized by Li \emph{et al.} \cite{li_optimization_2018} which is different from the MSBR-like model adopted by Cui \emph{et al.}; (4) Cui \emph{et al.} studied the high-enriched uranium (e$>$90) while we excluded it due to the unavailability of this material for use as an initial reactor fuel (non-proliferation issues) and because the performance of this material is expected to be similar to $^{233}$U; (5) Cui \emph{et al.} introduced two scenarios for thorium fuel cycle transition: a Breeding and Burning (B\&B) scenario and a Pre-breeding scenario while we adopting different approach by introducing two different feed mechanisms: thorium and non-thorium feed mechanism.

                Comparing with Cui \emph{et al.}, we used different geometry, volumes, densities, and fuel salt compositions. In Cui's scenarios, the amount of Th is kept constant. $^{233}$U is fed only in (B\&B) scenario and extra fissile materials would have to be added into the core if the produced $^{233}$U is not enough to maintain the reactor criticality. In the Pre-breeding scenario, all the $^{233}$U produced from the decay of the extracted $^{233}$Pa stored outside the core until it reaches the required startup mass for a new reactor. Thus, the criticality of the core is maintained by refueling external fissile material. 
                In current work, using the thorium feed mechanism, we simultaneously feed Th and all or part of produced $^{233}$U from the \texttt{Pa-decay tank} into the core. The excess $^{233}$U (if exist) is stored outside the core. In the non-thorium feed mechanism, we continuously inject external heavy metals (HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) and part of produced $^{233}$U from the \texttt{Pa-decay tank}. Here we feed a part of produced $^{233}$U because in some cases (e.g., TRU) refueling only external heavy metals failed to maintain the core criticality (limitation is dm$_{total fuel}$ $\leq$ 0.1\%). In the non-thorium feed mechanism, the amount of Th decreases during reactor operation while it is constant in the thorium feed mechanism.

@@

        \end{solution}

        %---------------------------------------------------------------------

        \question More details should be provided to illustrate the heavy metal addition for the thorium feed mechanism and non-thorium feed mechanism in page 11. It is hard to understand why the mass of Th / external heavy metals (excluding Th) is approximately equal to the mass of extracted Pa.
        \begin{solution}
               Thank you for the comment. Actually, in page 11, we mention 
               that the mass of Th / external heavy metals is approximately 
               equal to the mass of extracted Fission products (FPs) and not 
               Pa. Because in both feed mechanisms (thorium and non-thorium) 
               we continuously added $^{233}$U and the mass of injected 
               $^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa 
               decays to $^{233}$U after $\approx$ 27 d). To keep the total 
               fuel mass almost constant, for \textbf{thorium feed mechanism}, 
               the mass of injected Th must be equal to the mass of extracted 
               FPs and for \textbf{non-thorium feed mechanism}, the mass of 
               injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade 
               Pu, or TRU) must be equal to the mass of extracted FPs.
               We rewrite the paragraph on page 11 to clarify this point:\\

@@

               \begin{enumerate}
               	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
               	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-decay tank}, respectively.
               	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
               	\subitem 3a. \textbf{Thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected Th $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
               	\subitem 3b. \textbf{Non-thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
               	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant (1/s).
               \end{enumerate}
               In both feed mechanisms (thorium and non-thorium) we continuously added $^{233}$U and the mass of injected $^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa decays to $^{233}$U after $\approx$ 27 d). To keep the total fuel mass almost constant, for \textbf{thorium feed mechanism}, the mass of injected Th must be equal to the mass of extracted FPs and for \textbf{non-thorium feed mechanism}, the mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) must be equal to the mass of extracted FPs.

        \end{solution}

        %--------------------------------------------------------------------

        \question Phenomenons presented in Figure 3 that K-eff for the case of Pu+HALEU firstly increases and then decreases, and the time to become subcritical for the case of reactor-grade Pu is longest (except the case of U-233) should be explained.
        \begin{solution}
                 Thank you for your insightful comment. Phenomenons presented 
                 in Figure 3 have been described in the manuscript.
                 The following paragraph and additional Figure~4 has been added to the manuscript:\\

                 For Pu+HALEU case, $k_{eff}$ firstly increases during the first $\approx$ $3$ EFPY and then gradually decreases. This is due to the conversion of $^{238}$U from HALEU into fissile plutonium, which often produces the majority of the neutrons until the transition to Th/$^{233}$U fuel cycle. Figure~4 shows the variation in fissile plutonium isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) inventory during reactor operation. For TRU and reactor-grade Pu, the fissile plutonium isotopes are gradually depleted, during operating (the fissile material is dominated by Pu in these cases). For HALEU case, the fissile material is dominated by $^{235}$U, however, $^{238}$U is converted into fissile plutonium. Therefore, the mass of fissile plutonium increases during operating but its value still relatively low. For Pu+HALEU case, the mass of the fissile plutonium isotopes increases within the first $\approx$ $3$ EFPY and then decreases. The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, $k_{eff}$ increases during the first $\approx$ $3$ years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.\\

@@

                 Figure~3 shows that the decrease in $k_{eff}$ for reactor-grade Pu case occurs at the much later operating time than for other cases because the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U. Nevertheless, this amount of the $^{233}$U is not enough to counteract the neutron absorption in the non-fissile Pu isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted.

        \end{solution}

        %--------------------------------------------------------------------
        \question In page 19, why the Pa extraction time was selected to be 30s since Pa is neither the gaseous FPs nor the non-dissolved metals?
        \begin{solution}
                  Thank you for the question. Specifically, Pa is removed from the fuel by chemical reprocessing into the \texttt{Pa-decay tank} to decay and produce $^{233}$U. The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U. Figure~8 shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR. The faster extraction of Pa from the core (RP = $30$ $s$) is required to achieve suitable core lifetime. Also, the greater production of $^{233}$U can be obtained with RP = $30$ $s$ instead of $10.59$ $d$. The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup. Therefore, we selected the RP = $30$ $s$. This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ 40 years). For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~5).

                  The following paragraph and additional Figure~8 has been added to the manuscript:\\

                  The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U. Figure~8 shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR. The faster extraction of Pa from the core (RP = $30$ $s$) is required to achieve suitable core lifetime. Also, the greater production of $^{233}$U can be obtained with RP = $30$ $s$ instead of $10.59$ $d$. The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup. Therefore, we selected the RP = $30$ $s$. This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ 40 years). For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~5).
        \end{solution}

@@

        %--------------------------------------------------------------------
        \question For Figure 9, it is inaccurate to state that the mass of U-233 reaches equilibrium after ~30 years, apparently from the figure, we can observe that the mass of U-233 for three of the cases still increase/decrease after 30 years.

        \begin{solution}
                Thank you for the excellent point. The statement has been removed from the text.
                Moreover, we rewrite the paragraph to clarify this point:\\

                Figure~11 demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases. For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ $1.7$ $t$ at the EOL. For reactor-grade Pu and TRU cases, the mass of $^{233}$U firstly, increases and after $\approx$ $35$ and $45$ years for Pu and TRU cases, respectively, decreases. The neutron spectrum shift during operating affects the inventory of $^{233}$U in the fuel salt. Harder neutron spectrum enhance $^{233}$U breeding from $^{232}$Th. For the reactor-grade Pu and TRU cases, during operating, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope; the neutron spectrum softens (low conversation of $^{233}$U from $^{232}$Th). However, for $^{233}$U case, the neutron spectrum is hardened at EOL due to the accumulation of Pu isotopes.

@@

				More changes in thermal neutron flux shape and magnitude 
				during the reactor operation for the $^{233}$U case are 
				observed in the inner core zone ($R\lesssim150$) than in the 
				outer core zone. In the outer core zone, significant changes 
				during reactor operation are observed for the thermal 
				neutron flux for the reactor-grade Pu case. In contrast, for 
				the TRU case, it is almost negligible. Additionally, 
				Figure~16 shows relatively significant changes in thermal flux 
				leakage from the core for the Pu (equilibrium composition) and 
				TRU (initial and equilibrium composition) cases. The SD-TMSR 
				core design was optimized for $^{233}$U  				
				\cite{li_optimization_2018}; thus, the core geometry (e.g., 
				channels lattice pitch) must be re-optimized for another type 
				of fuel to obtain better neutronics performance.
        \end{solution}

        %--------------------------------------------------------------------
        \question Regarding to the FTC for three different cases, reasons should be provided to explain why spectrum softening will positively affects the FTC since generally harder neutron spectrum would benefit FTC.
        \begin{solution}
                Thank you for your insightful comment.  Indeed, the Doppler 
                effect coefficient ($\alpha_{D,F}$) is usually stronger for 
                harder spectrum (see Table~8, ``Fuel salt temperature''), so, 
                spectrum softening negatively affects $\alpha_{D,F}$ (it is 
                decreasing by value but still negative). But we additionally 
                considered the fuel salt density coefficient 
                ($\alpha_{\rho,F}$), which is usually positive in thermal MSRs 
                (e.g., $+1.09$ $pcm/K$ for the \gls{MSBR}           
                \cite{robertson_conceptual_1971}) and \textbf{softer} neutron 
                spectrum benefit $\alpha_{\rho,F}$ \cite{li_effects_2018-1, 
                rykhlevskii2019modeling}. More analysis on this topic:
            Li, X., Ma, Y., Yu, C. et al. Effects of fuel salt composition on 
            fuel salt temperature coefficient (FSTC) for an under-moderated 
            molten salt reactor (MSR). NUCL SCI TECH 29, 110 (2018). 
            https://doi.org/10.1007/s41365-018-0458-1.

### 2020-02-25 paper/results.tex
Osama comments addressed

The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U. Figure~\ref{fig:Keff_U2332} shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR. The fast extraction of Pa from the core (RP = $30$ $s$) leads to long operating time. Also, a relatively large amount of $^{233}$U can be obtained when we applied RP = $30$ $s$ against $10.59$ $d$. The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup. Therefore, we selected the RP = $30$ $s$. This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ $40$ years). For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~\ref{fig:keff2}).

@@

Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases. For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ $1.7$ $t$ at the EOL. For reactor-grade Pu and TRU cases, the mass of $^{233}$U firstly, increases and after $\approx$ $35$ and $45$ years for Pu and TRU cases, respectively, decreases. The neutron spectrum shift during operating affects the inventory of $^{233}$U in the fuel salt. Hard neutron spectrum converts more $^{233}$U from $^{232}$Th. For the reactor-grade Pu and TRU cases, during operating, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope; the neutron spectrum softens (low conversation of $^{233}$U from $^{232}$Th). However, for $^{233}$U case, the neutron spectrum is hardened at EOL due to the accumulation of Pu isotopes.

@@

\subsection{Neutron spectrum}
Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
lethargy for a full-core SD-TMSR model in the energy range from 10$^{-8}$ to 
10 MeV for the $^{233}$U, reactor-grade Pu, and TRU cases at BOL and EOL. In 
the $^{233}$U case, at the EOL, the neutron spectrum is harder than at BOL due 
to the accumulation of Pu and other strong thermal neutron absorbers in the 
fuel salt. For the reactor-grade Pu and TRU cases, during reactor operation, 
the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
(see Figure~\ref{fig:U233CC}); the neutron spectrum softens and becomes 
similar to the initial thermal spectrum of a $^{233}$U fueled SD-TMSR.
The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U. $^{232}$Th has a very high absorption cross section in the thermal region ($\approx10^2 $b). Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~\ref{fig:spectrumFLUX110vC}).
 \begin{figure}
 	\centering
 	\includegraphics[width=1.01\textwidth]{spectrumFLUX110vC.png}
 			\vspace{-0.4in}
 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for 3 different initial 
 		fuel salt compositions (for all cases, the neutron flux
 		confidence intervals $\pm\sigma$ at BOL and EOL are $<1.0139$\% and $<0.6274$\%, respectively).}
 	\label{fig:spectrumFLUX110vC}
\end{figure}

@@

Notably, the neutron flux change for both the fast and thermal energies is 
much larger for the reactor-grade Pu case than for TRU case 
(Figures~\ref{fig:fast_flux} and \ref{fig:thermal_flux}). The reason is the 
much softer neutron spectrum for the TRU initial loading compared with the 
reactor-grade Pu as shown in Figure~\ref{fig:spectrumFLUX110vC}: peak thermal 
neutron flux is about 4 times larger for the TRU case. The neutron spectrum in 
the SD-TMSR core initially loaded by TRU is much softer than the reactor-grade 
Pu case and even than the U-233 case because $^{232}$Th inventory is the 
lowest for the TRU case: 54.4t instead of 67.5t  and 76.9t for the  
reactor-grade Pu and U-233 cases, respectively (Table~\ref{tab:table5}). 
$^{232}$Th greatly affects the neutron energy spectrum due to its large 
absorption cross section in the thermal energy range and resonance region 
between $10^{-5}$ and $10^{-3}$. Finally, when the TRU and the reactor-grade 
Pu cases reached equilibrium fuel salt composition ($\approx 30$ years after 
startup), the radial fast and thermal neutron flux distribution became similar 
in both shape and magnitude.

>>>>

The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U. Figure~\ref{fig:Keff_U2332} shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR. The faster extraction of Pa from the core (RP = $30$ $s$) is required to achieve suitable core lifetime. Also, the greater production of $^{233}$U can be obtained with RP = $30$ $s$ instead of $10.59$ $d$. The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup. Therefore, we selected the RP = $30$ $s$. This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ $40$ years). For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~\ref{fig:keff2}).

@@

Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases. For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ $1.7$ $t$ at the EOL. For reactor-grade Pu and TRU cases, the mass of $^{233}$U firstly, increases and after $\approx$ $35$ and $45$ years for Pu and TRU cases, respectively, decreases. The neutron spectrum shift during operating affects the inventory of $^{233}$U in the fuel salt. Harder neutron spectrum enhance $^{233}$U breeding from $^{232}$Th. For the reactor-grade Pu and TRU cases, during operating, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope; the neutron spectrum softens (low conversation of $^{233}$U from $^{232}$Th). However, for $^{233}$U case, the neutron spectrum is hardened at EOL due to the accumulation of Pu isotopes.

@@

\subsection{Neutron spectrum}
Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
lethargy for a full-core SD-TMSR model in the energy range from 10$^{-8}$ to 
10 MeV for the $^{233}$U, reactor-grade Pu, and TRU cases at BOL and EOL. In 
the $^{233}$U case, at the EOL, the neutron spectrum is harder than at BOL due 
to the accumulation of Pu and other strong thermal neutron absorbers in the 
fuel salt. For the reactor-grade Pu and TRU cases, during reactor operation, 
the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
(see Figure~\ref{fig:U233CC}); the neutron spectrum softens and becomes 
similar to the initial thermal spectrum of a $^{233}$U fueled SD-TMSR.
The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U. $^{232}$Th has a very high absorption cross section in the thermal region ($\approx$ $10^2$ b). Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~\ref{fig:spectrumFLUX110vC}).
 \begin{figure}
 	\centering
 	\includegraphics[width=1.01\textwidth]{spectrumFLUX110vC.png}
 			\vspace{-0.4in}
 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for 3 different initial 
 		fuel salt compositions (for all cases, the neutron flux
 		confidence intervals $\pm\sigma$ at BOL and EOL are $<1.0139$\% and $<0.6274$\%, respectively).}
 	\label{fig:spectrumFLUX110vC}
\end{figure}

@@

Notably, the neutron flux change for both the fast and thermal energies is 
much larger for the reactor-grade Pu case than for TRU case 
(Figures~\ref{fig:fast_flux} and \ref{fig:thermal_flux}). The reason is the 
much softer neutron spectrum for the TRU initial loading compared with the 
reactor-grade Pu as shown in Figure~\ref{fig:spectrumFLUX110vC}: peak thermal 
neutron flux is about 4 times larger for the TRU case. The neutron spectrum in 
the SD-TMSR core initially loaded by TRU is much softer than the reactor-grade 
Pu case and even than the U-233 case because $^{232}$Th inventory is the 
lowest for the TRU case: $54.4$ $t$ instead of $67.5$ $t$ and $76.9$ $t$ for the  
reactor-grade Pu and U-233 cases, respectively (Table~\ref{tab:table5}). 
$^{232}$Th greatly affects the neutron energy spectrum due to its large 
absorption cross section in the thermal energy range and resonance region 
between $10^{-5}$ and $10^{-3}$. Finally, when the TRU and the reactor-grade 
Pu cases reached equilibrium fuel salt composition ($\approx 30$ years after 
startup), the radial fast and thermal neutron flux distribution became similar 
in both shape and magnitude.
